---
title: "data605 hw15"
author: "Jun Pan"
date: "May 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stats)
library(ggplot2)
```


#Problem 1
Find the equation of the regression line for the given points. Round any final values to the nearest hundredth, if necessary.

$(5.6, 8.8), (6.3, 12.4), (7, 14.8), (7.7, 18.2), (8.4, 20.8)$

#Solution
```{r}
df <- data.frame(x = c(5.6, 6.3, 7, 7.7, 8.4), y = c(8.8, 12.4, 14.8, 18.2, 20.8))
mod <- lm(y ~ x, data=df)
summary(mod)

ggplot(df, aes(x, y)) +
  geom_point(color = "green", alpha=0.5, size = 3) +
  geom_abline(aes(slope = coef(mod)[2], intercept = coef(mod)[1], color="red"))
```

Equation: $y = -14.8 + 4.26x $




#Problem 2

Find all local maxima, local minima, and saddle points for the function given below. Write your answer(s) in the form
$(x, y, z)$. Separate multiple points with a comma.

$f(x, y) = 24x - 6xy^2 - 8y^3$

#Solution

Partial derivatives:

$df/dx = 24-6y^2$
$df/dy = -12xy-24y^2$

$d^2f/dx = 0$
$d^2f/dy = -12x-48y$

$df/dx = 24-6y^2 = 0 -> 4-y^2=0$
$df/dy = -12xy-24y^2 = 0 -> -xy-2y^2=0$

y=+/-2.  when y=2 then x=-4 and when y=-2 then x=4.  So our points are (4,-2) and (-4,2).

for (4,-2)
$f(x,y) = 24*4-6*4*(-2)^2-8(-2)^3 = 64$ which is > 0

for (-4,2)
$f(x,y) = 24*-4-(6*-4*(2)^2)-8(2)^3 = -64$ which is < 0

Therefore, only (-4,2) is the saddle point.


#Problem 3
A grocery store sells two brands of a product, the "house" brand and a "name" brand. The manager estimates that if she sells the "house" brand for $x$ dollars and the "name" brand for $y$ dollars, she will be able to sell $81 - 21x + 17y$ units of the "house" brand and $40 + 11x - 23y$ units of the "name" brand.

Step 1. Find the revenue function $R ( x, y )$.
Step 2. What is the revenue if she sells the "house" brand for \$2.30 and the "name" brand for \$4.10?


$$
Rev = price * units sold \\
R_1(x) = x * (81 - 21x + 17y) = (81x -21x^2 + 17xy) \\
R_2(y) = y * (40 + 11x -23y) = (40y + 11xy = 23y^2)
$$


Revenue
$$
R(x,y) = 81x - 21x^2 + 17xy + 40y + 11xy -23y^2 \\
R(x,y) = -21x^2 + 28xy - 23y^2 + 81x +40y
$$

```{r}
r.xy <- function(x, y) -21*x^2 + 28*x*y - 23*y^2 + 81*x + 40*y

r.xy(2.3, 4.1)
```



#Problem 4
A company has a plant in Los Angeles and a plant in Denver. The firm is committed to produce a total of 96 units of a
product each week. The total weekly cost is given by $C(x, y) = \frac{1}{6} x^2 + \frac{1}{6} y^2 + 7x + 25y + 700$, where $x$ is the number of units produced in Los Angeles and $y$ is the number of units produced in Denver. How many units should be produced in each plant to minimize the total weekly cost?

#Solution
Consider $x+y=96$, then $x=96-y$.

$$
\begin{split}
C(x,y) = C(96-y,y) &= \frac{1}{6} x^2 + \frac{1}{6} y^2 + 7x + 25y + 700 \\
&=\frac{1}{6} (96-y)^2 + \frac{1}{6} y^2 + 7\times (96-y) + 25y + 700 \\
&=\frac{1}{6}(y^2 - 192 y + 9216) + \frac{1}{6}y^2+672-7y+25y+700\\
&= \frac{1}{6}y^2 - 32y+1536+\frac{1}{6}y^2+18y+1372\\
&= \frac{1}{3}y^2 - 14y + 2908\\
&=C_1(y)
\end{split}
$$
$C_1'(y) = \frac{2}{3}y-14$

For minimum value,
$C_1'(y)=\frac{2}{3}y-14=0$,
then, $y=21$,
then, $x=96-y=75$.

So, in order to miniumize the cost, 75 units should be produced in Los Angeles and 21 units should be produced in Denver.





#Problem 5

Evaluate the double integral on the given region.

$$
\int\int_R (e^{8x+3y}) dA, R:2\le x\le4\ and\ 2 \le y \le 4
$$
Write your answer in exact form without decimals.
#Solution


$$
\begin{split}
\int_2^4\int_2^4 (e^{8x+3y})\ dy\ dx &= \int_2^4 (\frac{1}{3}e^{8x+3y})|_2^4\ dx\\
&= \int_2^4 ((\frac{1}{3}e^{8x+12})-(\frac{1}{3}e^{8x+6}))\ dx\\
&= \int_2^4 \frac{1}{3}e^{8x+6}(e^6-1)\ dx\\
&=  \frac{1}{24}e^{8x+6}(e^6-1) |_2^4\\
&= \frac{1}{24}e^{32+6}(e^6-1)-\frac{1}{24}e^{16+6}(e^6-1)\\
&= \frac{1}{24}(e^6-1)(e^{38}-e^{22})\\
&= \frac{1}{24}(e^{44} - e^{38} - e^{28} + e^{22})
\end{split}
$$

